---
title: "Bivariate PIT"
author: "Mark Orndorff"
date: "08/28/2014"
output: html_document
---

The probability integral transform is the following theorem: Given R.V. X with CDF F,
F-1(X)~U(0,1). 

This theorem can be used to test goodness of fit. Under
H0: X ~ F, F-1(X) should be normally distributed. 

A short prototyping of a two sample version of this is developed here. A preliminary methodology is as follows. 
1) Combine both samples
2) Do linear interpolation of the ECDF to create a hypothesized null distribution (several options here with interpolation)
3) Assess the fit of the distributions by doing a PIT using the interpolated ECDF
4) Assess the uniformity of the results

This methodology has several problems:
1) The linear interpolated CDF is not the generating CDF, therefore we cannot expect the result of the PIT to be precisely normally distributed
2) We end up with two p-values (one from the 1st sample, one from the 2nd sample).

```{r}

```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
